% !TeX spellcheck = en_GB
\documentclass[a4paper, 11pt]{article}
%\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}

%margin
\usepackage[margin=2cm]{geometry}
%\usepackage[margin=1in]{geometry}
\usepackage{changepage}
%line spacing
\renewcommand{\baselinestretch}{1.15}
%\renewcommand{\baselinestretch}{1.6}
%lists
\usepackage{enumitem}
%multi-columns
\usepackage{multicol}
%encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%English
\usepackage[english]{babel}
%colors
\usepackage[dvipsnames,svgnames,table]{xcolor}
%tables
\usepackage{multirow}
\usepackage{longtable}
%for math
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{nicefrac}
\usepackage{makecell}
%for images
\usepackage{graphicx}
\graphicspath{ {./img/} }
%for plots
\usepackage{tikz}
\usetikzlibrary{mindmap}
\usepackage{adjustbox}
%links
\usepackage[hyphens]{url}
\usepackage{hyperref}
%\hypersetup{colorlinks=true}
%citations
\usepackage[square]{natbib}
\bibliographystyle{unsrtnat}
%code
\usepackage{minted}
\usepackage{algpseudocode}
\definecolor{CodeColor}{RGB}{100, 100, 100}
%files tree architecture
\usepackage{dirtree}



%environments
\newtheorem*{notation}{Notation}
\newtheorem{definition}{Definition}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{property}{Property}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[section]
\newtheorem{conjecture}{Conjecture}
%commands
%\newcommand{\name}[num]{definition}
\newcommand{\primes}{\mathbb{P}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\D}{\mathbb{D}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\halfplane}{\mathbb{H}}
%\newcommand{\dim}[1]{\text{dim}(#1)}
\newcommand{\SL}[2]{\text{SL}_{#1}(#2)}
\newcommand{\Norm}[2][]{\text{Norm}_{#1}(#2)}
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\abs}[1]{| #1 |}
\newcommand{\curt}[1]{\sqrt[3]{#1}}
\newcommand{\Ker}[1]{\text{Ker}(#1)}
\newcommand{\Image}[1]{\text{Im}(#1)}
\newcommand{\Gal}[1]{\text{Gal}(#1)}
\newcommand{\Frob}[2]{\text{Frob}_{#1}(#2)}
\newcommand{\Tr}[1]{\text{Tr}(#1)}
\newcommand{\Det}[1]{\text{Det}(#1)}
\newcommand{\End}[1]{\text{End}(#1)}
\newcommand{\Aut}[1]{\text{Aut}(#1)}
\newcommand{\legendre}[2]{\left( \frac{#1}{#2} \right)}
\newcommand{\degree}[1]{\partial #1}




\begin{document}
	\include{title_page}
	\begin{center}
		\LARGE Modular Forms Modulo 2
	\end{center}
	\vspace{0.5cm}
	\begin{abstract}
		Modular forms are functions over the upper half plane that play a prominent role in mathematics.
		Studying their properties over finite fields can yield useful information about the arithmetic of their Fourier coefficients.
		In this paper, we study modular forms over the smallest field of all, containing only an additive identity and a multiplicative identity, that is, $\F_2$.
		
		After introducing modular forms over the complex numbers, we will show how to reduce modular forms modulo 2.
		In this setting, modular forms may be seen as polynomials in the modular discriminant $\Delta$ or as power series in $q=\exp(2\pi i z)$. The duality between these two representations is crucial and we will use it in the development of a new computing technique: exact computations.
		
		We will then concentrate on the study of prime Hecke operators $T_p$ acting on modular forms modulo 2.
		These operators are nilpotent, with respect to a given modular form. The order of nilpotency is known, and we will discuss it.
		A Hecke operator $T_p$ at an odd prime $p$ acting on odd powers of $\Delta$ may also be expressed as power series in $T_3$ and $T_5$.
		
		The coefficient of $T_3^{i}T_5^{j}$ of this power series is denoted by $a_{ij}(p)$, and it will play a particularly important role in our study.
		The map $p \mapsto a_{ij}(p)$ is in fact Frobenian.
		We will try to discover new governing fields for these maps.
		
		In the last section, we will discuss the computing techniques developed to achieve the various computations performed.
	\end{abstract}
	\tableofcontents
	
	\include{Introduction}
	\include{ModularForms}
	\include{ModularFormsModuloTwo}
	\include{HeckeAlgebra}
	\include{FrobenianMaps}
	\include{Numerics}
	\appendix
	\include{title_appendix}
	\include{ComputationTables}
	\include{Codes}
	\include{GoverningFields}
	
	\bibliography{references}
\end{document}
